Supporting Information

### 2018-04-12 SupportingInformation.Rmd
new sections added for causes after meeting between Dan and Shyamolina

# Question 2 analyses for each dataset
Recall that question 2 is: What are some possible causes of non-Gaussian copula structure?

>>>>

# Question 2 analyses 
Recall that question 2 is: What are some possible causes of non-Gaussian copula structure?

## The Moran effect and copula structure in populations

We show here that if a non-normal copula structure describes the dependence of an environmental
variable between two locations, then there can be a non-normal copula structure for the
dependence of populations in the locations that are influenced by the environmental variables.

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->

## Asymmetric sensitivity and copula structure in populations

<!--Another model, distinct from the above, Dan and Shya to discuss-->

## Need to think about mechanisms for biogeochemical, evolutionary, and community data
